---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fars)
library(dplyr)
list.files(system.file("extdata", package = "FARS"))
```

This package contains a bunch of methods that make more convenient to work with FARS casualty data. At the very highest level, this package can be used to construct a scatter plot of accidents overlaid on an outline of the state where they occurred. For example, the code:

```{r}
fars_map_state("06", 2013)
```

Shows accidents in the state of California in 2013. You can see the state codes here: https://en.wikipedia.org/wiki/List_of_U.S._state_and_territory_abbreviations

Other features include the ability to summarize accident data for a particular year:

```{r}
fars_summarize_years(2013)
```

The ability to read in accident data for a bunch for a bunch of years at once:

```{r}
fars_read_years(c(2013, 2014, 2015))
```

Along with low level utility functions that can convert a year into the corresponding FARS file name:
```{r}
make_filename(2013)
```

And a function that can read in a specific file:
```{r}
fars_read("accident_2013.csv.bz2")
```
